---
title: "ETF_data_mining"
author: "Rafael Oliveira"
date: "5/25/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---
#CTRL+ALT+I to create new chunk

#Libraries
```{r setup, include=FALSE}
install.packages("selectr")
install.packages("xml2")
install.packages("rvest")
install.packages("jsonlite")
library(xml2)
library(rvest)
library(stringr)

```


#References
```{r}
#https://www.freecodecamp.org/news/an-introduction-to-web-scraping-using-r-40284110c848/
#https://www.dataquest.io/blog/web-scraping-in-r-rvest/
#https://swcarpentry.github.io/r-novice-inflammation/02-func-R/
#https://towardsdatascience.com/web-scraping-tutorial-in-r-5e71fd107f32
#https://www.freecodecamp.org/news/an-introduction-to-web-scraping-using-r-40284110c848/
```


#My ETFs
```{r}
my_ETFs = c("IE0005042456",
            "IE00B5BMR087", 
            "IE00BTJRMP35",
            "IE00B0M63177",
            "IE00B1YZSC51",
            "IE00BYZK4776",
            "IE00BYVQ9F29",
            "IE00BYXG2H39",
            "IE00B3WJKG14",
            "IE00B0M62Q58",
            "LU1781541179",
            "FR0007052782",
            "LU0252633754",
            "LU0496786574",
            "IE00BYTRRB94",
            "IE00BYTRRD19",
            "IE00B6YX5C33",
            "IE00BH4GPZ28",
            "IE00BWBXM948",
            "IE00BK5BQT80",
            "IE00B3VVMM84",
            "IE00B945VV12",
            "IE00B3XXRP09",
            "IE00B810Q511",
            "IE00BGV5VN51",
            "IE00BZ02LR44",
            "IE00BG370F43",
            "IE00BTJRMP35",
            "LU1681046931",
            "LU1681045370",
            "LU1681043599",
            "LU1681048804",
            "IE00BRKWGL70",
            "IE00B5BMR087",
            "IE00B0M63177",
            "IE00B1YZSC51",
            "IE00B4K48X80",
            "IE00BZCQB185",
            "IE00B4L5Y983",
            "IE0031442068",
            "IE00B53SZB19",
            "LU0252633754",
            "IE0032077012",
            "IE00BYVJRP78")
```


#Web Scraper
```{r Web Scraper, echo=TRUE, message=TRUE, warning=TRUE}
automatic = function(ETF) {
      ETF = read_html(paste0('https://www.justetf.com/de-en/etf-profile.html?query=',ETF,'&groupField=index&from=search&isin=',ETF,'#overview'))
      ETF = ETF %>%
            html_nodes(".h1,.val") %>% html_text()
      return(ETF)
}
```

#Info Retrieval and Storage
```{r Info Retrieval, echo=TRUE, message=TRUE, warning=TRUE}
loop = sapply(my_ETFs, automatic)

Data = as.data.frame(do.call(cbind, loop), stringsAsFactors = TRUE) #do.call takes a function as input and splatters its other arguments to the function. It is widely used, for example, to assemble lists into simpler structures (often with rbind or cbind)

final_data = Data[-c(1,3,14,15:30),] #remove unnecessary rows
View(final_data)
Data_complete = row.names(final_data) = c("Name","Ticket","Price","Fund Size","Replication","Type","Currency","Volatility","TER","Distribution","Fund Domicile")
Data_complete
final_data_switch = t(final_data) #t will switch the rows with columns and vice-versa
View(final_data_switch)

final_data_switch[final_data_switch$Distribution == "Accumulating"]


final_data_switch = as.data.frame(paste0('https://www.justetf.com/de-en/etf-profile.html?query=',ETF2,'&groupField=index&from=search&isin=',ETF2,'#overview'))
```



###################################################################################
final_data_switch = t(final_data)
View(final_data_switch)

str_replace_all(final_data, "[\r\n]", "")


#Name
automatic1 = function(ETF) {
      ETF = read_html(paste0('https://www.justetf.com/de-en/etf-profile.html?query=',ETF,'&groupField=index&from=search&isin=',ETF,'#overview'))
      ETF = ETF %>%
            html_nodes(".h1") %>% html_text()
      return(ETF)
}
#paste0 will link the strings with the variable I want to have in my input 

loop1 = sapply(my_ETFs, automatic1)
Data1 = as.data.frame(do.call(cbind, loop1))
View(Data1)
final_data1 = Data1[-c(2),]
Data_complete1 = row.names(final_data1) = c("Name")
final_data1_switch = t(final_data1)
View(final_data1)
View(final_data1_switch)

